A fast algorithm for computing best response strategies in two-person sequential games

### 2014-07-26 paper.tex
more

>>>>

\begin{remark}
The derivation above reveals that in equation \eqref{eq:opt_pb} above, if the constraint ``$x \ge 0$'' is replaced by
a constraint ``$x \in C$'' (thus obtaining a new problem) where $C$ is a convex set onto which euclidean projections
can be easily computed (for example, a probability simplex), then we simply need to replace the operator ``$(.)_+$''
with ``$\Pi_C$'' in the equations to obtain a corresponding algorithm.
\end{remark}
